---
title: "PSET3"
author: "Aziz Goziev"
date: '2022-05-06'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Load the ak91.csv data
df<-read.csv ("ak91.csv" )
n<-nrow(df)

# Store years of education and the weekly wage in separate variables
yrs_educ <- df$YRS_EDUC
wkly_wage <- df$WKLY_WAGE

```

#Question 6a.)
```{r}
beta <- cov(wkly_wage, yrs_educ) / var(yrs_educ)
alpha <- mean (wkly_wage) - mean (yrs_educ) * beta
beta
alpha
```

#Question 6b.)
29.6224=alpha
61.19=beta

An additional year of education is associated with an approximately $61.19 increase in weekly wages.

#Question 6c.) 
```{r}
blp_yx=alpha+16*beta
blp_yx
```
The result does differ from 5b in pset 2 because our estimate is an approximation to the CEF function.

#Question 6d.)
```{r}
blp_yx=alpha+beta*yrs_educ
epsilon<- wkly_wage - blp_yx
se_numer <- sqrt(mean(epsilon^2 * (yrs_educ - mean(yrs_educ))^2))
se <- (se_numer/var(yrs_educ))/sqrt(n)
se
```

#Question 6e.)
```{r}
t_statistic<-(beta-31)/se
t_statistic
```
#Question 6f.)
```{r}
p_value<-pnorm(t_statistic)
p_value
```

#Question 6g.)
Yes we reject the null hypothesis at the 10% significance level. This means at the 10% significance level there is evidence that the approx expected change in weekly wages due to an associated unit change in number of years of education is not $31.
