---
title: "Pset4"
author: "Aziz Goziev"
date: '2022-05-22'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Load the bw06.csv data
dat<-read.csv("C:/Users/azizg/Downloads/College/3rd Year/2022 Spring Quarter/Econometrics/Datasets/bw06.csv")
dat<-as.matrix(dat)
```

```{r}
# Select variables
y <- dat[, "birthweight"]
w <- dat[, "cigsdaily"]
x <- cbind(1, dat[, c("boy", "age", "highschool", "somecollege", "college")])
x_tld <- dat[,"married"]

```

Part A 
```{r}
beta_w <- cov(y, w) / var(w)
alpha <- mean (y) - mean (w) * beta_w
beta_w
alpha
```
The beta here represents the approximate expected change in birth weight associated with an additional cigarette smoked per day by the child's mother.

Part B
```{r}
x<-cbind(x,w)
xx_inv<-solve(t(x) %*% x)
yx<- t(x) %*% y
beta_yx<-xx_inv %*% yx
beta_yx[length(beta_yx)]
```
This beta here represents the approximate expected change in birth weight associated with an additional cigarette a day controlling for gender, education, and age.

Part C


Yes, our estimates differ. This is due to the second beta being controlled for other factors that explain the variation in the outcome factors.

Part D

They are wrong because we haven't made an identifying assumption in this estimation that can warrant causality, this is merely an association between two variables.

Part E


Common support states suppX=suppX|W, which means for every set of observables there are individuals at every level of W=w'.

Selection on observables assumes W is independent of U|X, which in this context means that weight of the baby is independent of all other unobservables and only depend on observables.

In this study, I don't think SO assumption is plausible as there are many other factors, such as genetic traits that aren't accounted for in our model.

Part F
```{r}
w<-dat[,"cigsdaily"]
x<-cbind(1,dat[,c("boy", "age", "highschool","somecollege", "college")])

X<-cbind(x,w)

all_true<-function(list){
  for(x in 1:length(list)){
    if(!list[x]){
      return(list[x])
    }
  }
  return(TRUE)
}

dupes<-X[duplicated(X),]
matches<-dupes[1,]
count<-0
for(row in 1:nrow(dupes)){
  if(all_true(dupes[1,-ncol(dupes)]==dupes[row,-ncol(dupes)]) & (count==1)){
    matches<-rbind(matches, dupes[row,])
  }
  else{
    if(count!=1){
      count<-1
    }
  }
}
```

```{r}
print(nrow(matches))
```
Num. of observations with same x as obs. 1 is 156.

```{r}
print(length(unique(w)))
```
Num. of total unique w.

```{r}
print(nrow(unique(matches)))
```
Unique values of w for same x.

Common support can't be verified for given x as there values of w that aren't covered in the sample. 


Q7.
Part A
```{r}
my_coef<- function(y, X){
  xx_inv<- solve(t(X) %*% X)
  yx<-t(X) %*% y
  beta<- xx_inv %*% yx
  return(beta)
}
my_coef<-my_coef(y,X)
my_coef
```

Part B
```{r}
my_blp<-function(coef, x){
  blp_xy <- x %*% coef
  return(blp_xy)
}

mean(y-my_blp(coef, X))
```
Part C
```{r}
my_se <- function(coef, y, X){
  num<-nrow(X)
  epsilon<-c(y - blp(coef, X))
  xx_inv<-solve(t(X) %*% X)
  xx_eps<-t(X*epsilon) %*% (X*epsilon)
  sig<-(xx_inv %*% xx_eps %*% xx_inv)*n
  se<-sqrt(diag(sig))/sqrt(num)
}

se<-my_se(coef, y, X)
se

```


Part D
```{r}
my_teststat <- function(beta, se){
  t<-abs(beta/se)
  p<-2*(1-pnorm(t))
  return(list(t,p))
}
my_teststat(coef, se)
```

Part E
```{r}

```

